\section{Description}
In this chapter we will give a short description of the game that we are making. Also, we will give more insight into the techniques we are using to make the game.

\subsection{Game}
We are working on an Age of Empires like game. The reason we chose for an Age of Empire like game is because features of such game are pretty modular. The basic idea of the game is this: the player has workers from various classes to collect different resources. The resources can be used to extend his village/city and build more units. ~\\
We are focusing on:
\begin{itemize}
  \item Building a settlement
  \item Starting with a static view
  \item Controlling the game feels somewhat intuitive
  \item Controlling units, e.g. sending workers to get resources
  \item GUI
  \item Writing a UI framework from scratch (this is a new technique for us)
\end{itemize}

If we have enough time we are also going to make an AI player that attacks the human player. Other features like:
\begin{itemize}
  \item Upgrading buildings
  \item Upgrading units
  \item Achieving a new age
  \item Combat system
  \item Nice graphics
  \item Smart AI
  \item Controlling the game feels natural
  \item Camera controls
\end{itemize}
will be implemented if time permits.

\subsection{Methods, techniques and languages}
The game is written in C++. We are also using the following methods and techniques.
\begin{itemize}
  \item Scrum
  \item \LaTeX
  \item Git
  \item Steering behaviours
  \item Fuzzy Logic
  \item Goal driven behaviour
  \item SDL
\end{itemize}