\section{Methods}
In this chapter we will give insight into the software development method and our testing strategy. 

\subsection{Scrum}
We are working based off the scrum framework. Because we do not have a product owner and no real stakeholders we only use the things we think are good for our work method. This means we have a daily meeting every morning we work on the project. Below we have listed the decisions we have made for our first sprint, this can be altered later so it is open for improvement, but this will be the skeleton for how we will do scrum during the project.
How we will do scrum:
\begin{itemize}
  \item Sprints of two weeks (Consists of eight working days at Windesheim).
  \item Daily scrum every working day at 10:00.
  \item Sprint planning at the start of the sprint.
  \item Discuss sprint results with the team at the end of each sprint.
  \item Short retrospective at the end of each sprint.
  \item Scrum master role will be filled in by Mark.
  \item Role of product owner will be filled in by the complete team.
\end{itemize}

\subsection{Test strategy}
We are going to test our user stories in different stages. First the producer of the code will test his own work before making a pull request. The producer will test if his own work meets the acceptance criteria and if the other user stories still work. After that, he will merge his branch with the development branch and solve any conflicts. After that the producer will test the code again. If it works it's ready for a pull request. When a pull request is made, the producer of the code will add new test cases to the test report. The reviewer will checkout the code and test it. Also, the reviewer will add results to the test cases in the test report that were added for that particular pull request.

~\\

We will make unit tests for the implemented user stories if we think it is testable, useful and necessary. We are using the Google Test C++ testing framework to write our unit tests. Even though we have a unit testing setup, the focus is primarily on functional tests.

\subsection{Tooling}
A lot of tooling is available for use in software development. We have chosen a set of tooling that we would like to use for this project. In this section we will explain the selection of tooling.

\paragraph{Telegram}
~\\ The chat application Telegram is be used to communicate with the group (or specific members of the group). A group chat has been created so that messages can be quickly shared with the group.

\paragraph{GitHub}
~\\ Git is used as the source control system. All code (and documents) is stored inside a GitHub repository. Branches are made for all changes and reviews will be done when a Pull Request is opened.

GitHub has a relatively new feature called "projects". A GitHub project consists of columns containing GitHub issues. This looks very similar to a tool called Trello. An example can be seen in \cref{fig:githubproject}. Since we use GitHub quite extensively, using a GitHub project as our product backlog is a nice fit.

\paragraph{Editors}
~\\ The group uses the Clion editor. 

\paragraph{TravisCI}
~\\ Since all our code is in a public GitHub repository, we can easily configure a build service using TravisCI. This build server compiles the game, run the linter and the unit tests. This makes the review process quicker.

